\documentclass[fleqn]{article}
\usepackage{enumitem}

\begin{document}

\begin{enumerate}[label=\textbf{\arabic*}]

  %exrcise 1 
	\item Identification of propositions and eventual truth values.  
  \begin{enumerate}[label=\textbf{\alph*)}]
    \item The sentence ``Boston is the capital of Massachusetts.'' is a proposition, the truth value is true.
    \item The sentence ``Miami is the capital of Florida.'' is a proposition, the truth value is false.
    \item $ 2 + 3 = 5 $ is a proposition, the truth value is true.  
    \item $ 5 + 7 = 10 $ is a proposition, the truth value is false.
    \item $ x + 2 = 11 $ is not a proposition.
    \item The sentence ``Answer this question.'' is not a proposition. 
  \end{enumerate}

  %exercise 2
  \item Identification of propositions and eventual truth values.
  \begin{enumerate}[label=\textbf{\alph*)}]
    \item The sentence ``Do not pass go.'' is not a proposition.
    \item The sentence ``What time is it?'' is not a proposition.
    \item The sentence ``There are no black flies in Maine.'' is a proposition, the truth value is false since there are black flies in Maine.
    \item $ 4 + x = 5 $ is not a proposition.
    \item The sentence ``The moon is made of green cheese.'' is a proposition, the truth value is false.
    \item  $ 2^n > 100 $ is not a proposition.
  \end{enumerate}
  
  %exercise 3
  \item 
  Some propositions and the corresponding negations.
  \begin{enumerate}[label = \textbf{\alph*)}]
  \item 
  Mei has an MP3 player.\\
  Mei does not have an MP3 player.
  \item
  There is no pollution in New Jersey.\\
  There is pollution in New Jersey.
  \item
  $2 + 1 = 3$\\
  $2 + 1 \neq 3$
  \item
  The summer in Maine is hot and sunny.\\
  The summer in Maine is not hot and sunny.
  \end{enumerate}
  
  %exercise 4
  \item
  Let $ p $ and $ q $ be the propositions
  
  \begin{enumerate}[label={}]
  \item
  $ p : $ I bought a lottery ticket this week.
  \item  
  $ q : $ I won the million dollar jackpot.
  \end{enumerate}
  
  Below follows some propositions based around the above propositions. Each proposition is accompanied  by an example of how it can be expressed as an English sentences.
  \begin{enumerate}[label = \textbf{\alph*)}]
  \item  
  $\neg p$ -- I did not buy a lottery ticket this week.  
  \end{enumerate}
\end{enumerate}
  
\end{document}